%-------------------------
% Resume in Latex
% Author : Yash Jajoo
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{#2} \\
    \end{tabular*}\vspace{-7pt}
}

% \newcommand{\resumeProjectHeadingTwo}[3]{
%     \item
%     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
%       \small#1 & \small#2 & \small#3 \\
%     \end{tabular*}\vspace{-7pt}
% }


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yash Jajoo} \\ \vspace{1pt}
    \small 716 (368)-8162 $|$ \href{mailto:yashjajo@buffalo.edu}{\underline{yashjajo@bufflo.edu}} $|$ 
    \href{https://linkedin.com/in/restacksyj}{\underline{linkedin.com/in/restacksyj}} $|$
    \href{https://github.com/restacksyj}{\underline{github.com/restacksyj}} $|$
    \href{https://restacksyj.com}{\underline{restacksyj.com}} 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      % {University at Buffalo, The State University of New York}{August 2024 -- December 2025}
      {University at Buffalo, The State University of New York}{Graduating December 2025}
      {Masters of Science, Computer Science}{Buffalo, NY}
    \resumeSubheading
      {Sinhgad Institute Of Technology, Lonavala}{August 2017 -- May 2021}
      {Bachelor of Engineering, Computer Science}{Pune, India}
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
            \textbf{Languages}{: Python, Golang, Typescript, Javascript, Dart, Rust, C, C++, PHP, Lua } \\ \textbf{Databases}{: MySQL, MongoDB, PostgreSQL, BigQuery, Redis} \\ \textbf{Frameworks/Others}{: Apache Kafka, Kubernetes, Docker, AWS, GCP, Git, React, Laravel, Azure, NodeJS, Flask, PyTorch, Spring Boot, Grafana, Nginx, GitOps, Debezium, Astro, Linux, Neovim, Jupyter Notebook }}}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Freightify}{August 2021 -- July 2024}
      {Software Development Engineer 2 $|$ Golang, NodeJS, MongoDB, AWS, React}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Scaled multiple products to support thousands of users, maintaining various microservices and employing modern
        tech-stacks such as \textbf{gRPC}, Golang, and NodeJS to develop highly available systems with \textbf{99.5\% uptime.}}
        \resumeItem{Modernized infrastructure by transitioning from traditional AWS EC2 to \textbf{Kubernetes} and Google Cloud Platform
        (GCP), improving scalability and \textbf{reducing deployment time by 40\%} through automated container orchestration and efficient resource management.}
        \resumeItem{Developed full-stack applications using the MERN stack, building internal tools that increased operational
        \textbf{efficiency by 30\%} and enhanced product management within the company.}
        \resumeItem{Implemented \textbf{ETL} pipeline using \textbf{distributed systems} such as \textbf{Kafka} and Debezium to stream real-time changes in the database and visualizing it in \textbf{Grafana} dashboards.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Occipital Tech}{October 2019 -- December 2019}
      {Software Engineering Intern $|$ Flutter, Java}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{
Engineered an Android and iOS application to empower farmers in identifying and grading commodity samples.}
\resumeItem{Implemented real-time analysis of features using \textbf{OpenCV} on Android to \textbf{optimize accuracy by 20\%.}} 
        \resumeItem{Designed an intuitive user interface to enhance \textbf {user engagement by 30\%} and streamlined the grading process.}
    \resumeItemListEnd


    \resumeSubheading
      {Freightbro Logistics}{August 2018 -- March 2019}
      {Software Engineering Intern $|$ Flutter, Swift, Kotlin, Dart}{Mumbai, India}
      \resumeItemListStart
      \resumeItem{Developed a logistics management Android app using Flutter, incorporating RxDart for \textbf{efficient state management} and \textbf{reactive programming}. The app facilitated real-time shipment tracking, order management, and notifications, ensuring a smooth user experience across devices.}
      \resumeItem{ Implemented complex \textbf{client-side logic with caching} to enhance application functionality and performance. }
        \resumeItem{Streamlined authentication processes and deployment workflows using Firestore and \textbf{CircleCI}, reducing deployment time by 45\% and improving overall app management efficiency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
  {\textbf{Lyrik} $|$ \emph{Flutter, NodeJS, Firebase} $|$ 
   \href{https://play.google.com/store/apps/details?id=com.buildjuice.lyriks\&hl=en\_US}{\underline{Play Store Link}}}
  {December 2019 -- Present}
          \resumeItemListStart
          \resumeItem{Engineered the Lyrik Android app, enabling users to search, view, and save song lyrics across various music genres. Implemented \textbf{offline} functionality using \textbf{SQLite} for seamless access without internet connectivity.}
            \resumeItem{
                Over \textbf{50,000+} downloads on the Google Play Store.
}
            \resumeItem{
                 Implemented real-time lyrics display, and playlist management features using Flutter and Dart; optimized performance and enhanced UI/UX, resulting in a \textbf{4.8-star} rating on the Google Play Store within three months of launch.	
}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Speech Emotion Detection} $|$ \emph{Python, PyTorch, scikit-learn, CNN}}{Decemeber 2020 -- May 2021}
          \resumeItemListStart
          \resumeItem{Utilized \textbf{LSTM and CNN} models to predict speech emotional states and classify them into six categories.}
            \resumeItem{Preprocessed raw audio data by extracting relevant features such as MFCC, pitch, and spectral contrast.}
            \resumeItem{Deployed the model on a website for practical emotion detection using real-time audio.}
            % \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          \resumeItemListEnd
    \resumeSubHeadingListEnd




% \\ \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
      % \textbf{Libraries}{: pandas, NumPy, Matplotlib}

%  REST API, FastAPI, Django, Apache Kafka, Airflow, Git, React, NodeJS, AWS, Redux, Webpack,
% Flask, MQTT, Azure, GraphQL, PyTorch, Tensorflow, Azure, Nginx, GCP, CI/CD, Docker, Kubernetes, Linux

%-------------------------------------------
\end{document}

